---
title: "High School Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
runtime: shiny 
---

<style>

.navbar {
background-color: #7F3800;
color: #fff;
border-color: #7F3800
}

.navbar-brand {
color:#fff!important;
}


.navbar-nav li a:hover, .navbar-nav > .active > a {
color: #fff !important;

background-color:#B35701 !important;
background-image: none !important;
}

div.dt-buttons {
    float: right;
}

.chart-wrapper {
background: #f2f5f7;
font-size : 15px;
border-radius: 10px;
}

body{
background: #3c4858;
font-size: 15px;
}

.chart-title {
    font-size: 15px;
    color: #fff;
    background-color: #7F3800;
    border-radius: inherit;
}

</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(dpi = 300)
library(flexdashboard)
library(tidyverse)
library(readr)
library(stringr)
library(lubridate)
library(colorspace)
library(DT)
library(ggmosaic)
library(shiny)
```


```{r functions}
## reset all timeseries 
reset <- function(){
  ts1<- readRDS("aca1_ts.RDS")
  ts1<- ts1[0,]
  saveRDS(ts1, "aca1_ts.RDS")
  
  ts2<- readRDS("aca2_ts.RDS")
  ts2<- ts2[0,]
  saveRDS(ts2, "aca2_ts.RDS")
  
  ts3<- readRDS("aca3_ts.RDS")
  ts3<- ts3[0,]
  saveRDS(ts3, "aca3_ts.RDS")
  
  ts4<- readRDS("att_ts.RDS")
  ts4<- ts4[0,]
  saveRDS(ts4, "att_ts.RDS")

  ts5<- readRDS("school_ts.RDS")
  ts5<- ts5[0,]
  saveRDS(ts5, "school_ts.RDS")
  }

## not in function
`%!in%` <- Negate(`%in%`)

## update timeseries
tsgrades_update <- function(ts_name, new_data, date){
  grades.df<- readRDS(ts_name)
  
  if (date %!in% grades.df$date){
    grades<- new_data %>% 
      mutate(grade = substring(grade, 0,1))%>% 
      group_by(grade)%>% 
      summarise(n=n())%>%
      pivot_wider(names_from = grade, values_from = n)
    
    grades<- data.frame(date = date, grades)
    grades.df<- bind_rows(grades.df,grades)
    saveRDS(grades.df, ts_name)
    }
  grades.df
  }

## plot grade timeseries

tsgrades_plot<- function(grades.df){
  renderPlot(
  grades.df %>%
    pivot_longer(cols = 2:6)%>%
    ggplot(aes(x=date, y=value, color=name))+
    geom_point(size=2)+
    geom_line(size=1)+
    scale_color_manual(values = rev(pal[c(1,2,4,6,7)]))+
    theme_classic()+
    labs(title="", col = "Grade")+
    expand_limits(x = ymd("2022-01-17"))+
    scale_x_date(date_breaks = "2 weeks")+
    theme(axis.title = element_blank(),
          panel.background = element_rect(fill = greys[4], color = greys[4]),
          plot.background = element_rect(fill = greys[4], color = greys[4]),
          legend.background = element_rect(fill = greys[4], color = greys[4]),
          legend.box.background = element_rect(fill = greys[4], color = greys[4])))
}

## Grades Bar graph
grades_bar<- function(df_full){
  p<- df_full%>% mutate(grade = substring(grade,0,1))%>%
    ggplot(aes(grade))+
    geom_bar(fill = pal[1], color = pal[1])+ 
    geom_text(aes(label=..count..), stat = "count", 
              vjust = -0.5, size=5)+
    theme(axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          axis.text.x = element_text(size = 14),
          axis.title = element_blank(),
          panel.background = element_rect(fill = greys[4], color = greys[4]),
          plot.background = element_rect(fill = greys[4], color = greys[4]),
          legend.background = element_rect(fill = greys[4], color = greys[4]),
          legend.box.background = element_rect(fill = greys[4], color = greys[4]), 
          panel.grid = element_blank())+ 
    scale_y_continuous(expand=expansion(mult = c(0, 0.15)))
  renderPlot(p)
  }

## plot grade percentage histogram facetted by grade level
grades_grade<- function(df_full){
  renderPlot(
    ggplot(df_full, aes(percent))+
    geom_histogram(fill = pal[1], color = pal[4], breaks = seq(0,110,10), na.rm = T)+ 
    scale_x_continuous(breaks = seq(0,110,10),
                       labels = paste(seq(0,110,10), "%", sep = ""))+
    theme(axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.text.x = element_text(size = 14),
          axis.title = element_blank(),
          panel.background = element_rect(fill = greys[4], color = greys[4]),
          plot.background = element_rect(fill = greys[4], color = greys[4]),
          legend.background = element_rect(fill = greys[4], color = greys[4]),
          legend.box.background = element_rect(fill = greys[4], color = greys[4]), 
          panel.grid = element_blank(),
          strip.background = element_rect(fill = greys[4], color = greys[4]),
          strip.text = element_text(size = 12, )
          )+
    facet_wrap(vars(Grade), ncol = 1))
}

## group attendence levels
att_data<- function(new_data){
  df_att<- new_data%>% 
    distinct(ID, .keep_all = T)%>%
    mutate(Attend2 = cut(Attend, breaks = c(0,25,50,60,80,90,100),
                         labels = paste( "gr", 
                                         c(0,25,50,60,80,90), 
                                         sep = "")))
  df_att
}

## load and update attendence timeseries
att_update <- function(att_ts, df_att){
  att.df<- readRDS(att_ts)
  
  if (date %!in% att.df$date){
    att<- df_att %>% 
      group_by(Attend2)%>% 
      summarise(n=n())%>%
      mutate(n = n/sum(n))%>%
      pivot_wider(names_from = Attend2, values_from = n)
    
    att<- data.frame(date, att)
    att.df<- bind_rows(att.df,att)
    saveRDS(att.df, att_ts)
  }
  att.df
}

## attendence timeseries plot
att_ts_plot<- function(att.df){
  p<- att.df %>%
    pivot_longer(cols = 2:ncol(att.df))%>%
    mutate(name = factor(name, 
                         levels = c('gr90', 'gr80','gr60',
                                    'gr50', 'gr25','gr0'  
                         ),
                         labels = c(">90%", ">80%", ">60%",
                                    ">50%", ">25%", ">0%")))%>%
    filter(!is.na(name))%>%
    ggplot(aes(x=date, y=value, color=name))+
    geom_point(size=2)+
    geom_line(size=1)+
    scale_color_manual(values = pal)+
    theme_classic()+
    labs(col = "Attendance")+
    expand_limits(x = ymd("2022-01-17"))+
    theme(axis.title = element_blank(),
          axis.text = element_text(size = 12),
          legend.text = element_text(size = 12),
          legend.title = element_text(size = 14),
          panel.background = element_rect(fill = greys[4], color = greys[4]),
          plot.background = element_rect(fill = greys[4], color = greys[4]),
          legend.background = element_rect(fill = greys[4], color = greys[4]),
          legend.box.background = element_rect(fill = greys[4], color = greys[4]), 
          panel.grid = element_blank()
    )+
    scale_y_continuous(breaks = seq(0,1,0.1), 
                       labels = paste(seq(0,100,10), "%", sep = ""))+
    scale_x_date(date_breaks = "2 weeks")
  
  renderPlot(p)
}

## Attendence by ethnicity plot
att_eth<- function(df_att){
  p<- df_att %>% group_by(ETHNICITY, Attend2)%>%
    summarise(n = n())%>%
    mutate(n = n/sum(n),
           Attend2 = factor(Attend2, 
                            levels = c('gr90', 'gr80','gr60',
                                       'gr50', 'gr25','gr0'  
                            ),
                            labels = c(">90%", ">80%", ">60%",
                                       ">50%", ">25%", ">0%")))%>%
    ggplot(aes(y = ETHNICITY, x = n, fill = as.factor(Attend2)))+
    geom_col()+
    scale_x_continuous(breaks = seq(0,1, 0.1),
                       labels = paste(seq(0,100, 10), "%", sep = ""))+
    theme_classic()+
    labs(fill = "Attendance")+
    theme(axis.title = element_blank(),
          legend.position = "right",
          axis.text.x = element_text(size = 12),
          axis.text.y = element_text(size = 12),
          legend.text = element_text(size = 12),
          legend.title = element_text(size = 14),
          panel.background = element_rect(fill = greys[4], color = greys[4]),
          plot.background = element_rect(fill = greys[4], color = greys[4]),
          legend.background = element_rect(fill = greys[4], color = greys[4]),
          legend.box.background = element_rect(fill = greys[4], color = greys[4]), 
          panel.grid = element_blank())+
    scale_fill_manual(values = rev(pal[1:5]))
  renderPlot(p)
}

## Attendence by grade level
att_grade<- function(df_att){
  p<- df_att %>% group_by(Grade, Attend2)%>%
    summarise(n = n())%>%
    mutate(n = n/sum(n),
           Attend2 = factor(Attend2, 
                            levels = c('gr90', 'gr80','gr60',
                                       'gr50', 'gr25','gr0'  
                            ),
                            labels = c(">90%", ">80%", ">60%",
                                       ">50%", ">25%", ">0%")))%>%
    ggplot(aes(x = Attend2, y = n, fill = as.factor(Grade)))+
    geom_col(position = "dodge")+
    scale_y_continuous(breaks = seq(0,1, 0.1),
                       labels = paste(seq(0,100, 10), "%", sep = ""))+
    theme_classic()+
    labs(fill = "Grade Level",
         x = "Attendance")+
    theme(axis.title.y = element_blank(),
          legend.position = c(.9, .8),
          axis.text = element_text(size = 12),
          axis.title.x = element_text(size = 14),
          legend.text = element_text(size = 12),
          legend.title = element_text(size = 14),
          panel.background = element_rect(fill = greys[4], color = greys[4]),
          plot.background = element_rect(fill = greys[4], color = greys[4]),
          legend.background = element_rect(fill = greys[4], color = greys[4]),
          legend.box.background = element_rect(fill = greys[4], color = greys[4]), 
          panel.grid = element_blank())+
    scale_fill_manual(values = rev(pal[1:4]))
  renderPlot(p)
}

## attendence by iep status
att_iep<- function(df_att){
  p<- df_att %>% group_by(IEP, Attend2)%>%
    summarise(n = n())%>%
    mutate(n = n/sum(n),
           Attend2 = factor(Attend2, 
                            levels = c('gr90', 'gr80','gr60',
                                       'gr50', 'gr25','gr0'  
                            ),
                            labels = c(">90%", ">80%", ">60%",
                                       ">50%", ">25%", ">0%")),
           IEP = factor(IEP, levels = c(TRUE, FALSE), labels = c("Yes", "No")))%>%
    ggplot(aes(x = Attend2, y = n, fill = as.factor(IEP)))+
    geom_col(position = "dodge")+
    scale_y_continuous(breaks = seq(0,1, 0.1),
                       labels = paste(seq(0,100, 10), "%", sep = ""))+
    theme_classic()+
    labs(fill = "IEP",
         x = "Attendance")+
    theme(axis.title.y = element_blank(),
          legend.position = c(.9, .8),
          axis.title.x = element_text(size = 14),
          axis.text = element_text(size = 12),
          legend.text = element_text(size = 12),
          legend.title = element_text(size = 14),
          panel.background = element_rect(fill = greys[4], color = greys[4]),
          plot.background = element_rect(fill = greys[4], color = greys[4]),
          legend.background = element_rect(fill = greys[4], color = greys[4]),
          legend.box.background = element_rect(fill = greys[4], color = greys[4]), 
          panel.grid = element_blank())+
    scale_fill_manual(values = pal[c(2,4)])
  renderPlot(p)
}

## histogram number of failing grades per student
fail_count<- function(df.f){
  m<-max(df.f %>% group_by(Number_F)%>% summarise(n=n()))
  renderPlot(
  ggplot(df.f, aes(Number_F))+
    geom_histogram(binwidth = 1, color=pal[4], fill=pal[1])+
    geom_text(aes(label=..count..), stat = "count",
              vjust=-.5, size=5)+
    scale_x_continuous(breaks = 0:8)+
    scale_y_continuous(limits = c(0,m+(0.05*m)))+
    labs(x="Number of Failing Classes")+
    theme(plot.title = element_text(size = 18),
          axis.title.x = element_text(size=16),
          axis.text.x = element_text(size=14),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          panel.background = element_rect(fill = greys[4], color = greys[4]),
          plot.background = element_rect(fill = greys[4], color = greys[4]),
          legend.background = element_rect(fill = greys[4], color = greys[4]),
          legend.box.background = element_rect(fill = greys[4], color = greys[4]), 
          panel.grid = element_blank()))
}


## create fail by hour data
hour_data <- function(df){
  df.hour<- df%>% count(hour)  
  
  df.fails.hour<- df %>% group_by(hour)%>%
    count(grade) %>% 
    left_join(df.hour, by = c("hour"))%>%
    mutate(rel_freq = n.x/n.y) %>% 
    filter(grade == "F")
  
  df.fails.hour
}

## Fail by hour plot
fail_hour <- function(df, avg.fail.school, avg.fail.aca = NA){
  df.hour<- df%>% count(hour)  
  
  df.fails.hour<- df %>% group_by(hour)%>%
    count(grade) %>% 
    left_join(df.hour, by = c("hour"))%>%
    mutate(rel_freq = n.x/n.y) %>% 
    filter(grade == "F")
  
  p<- ggplot(df.fails.hour, aes(x= hour, y=rel_freq))+
    geom_col(fill = pal[1], color = pal[4])+
    geom_hline(yintercept =avg.fail.school, col = pal[3], size = 1)+
    geom_text(aes(label = paste(round(rel_freq, 3)*100,"%")), 
              vjust = -.5, size = 5)+
    annotate(geom = "text", y= Inf, x=Inf, 
             label= paste("Avg Fail Rate:",round(avg.fail.school, 3)*100, "%"),
             vjust=1, hjust=1, color=pal[3], size=4)+
    scale_x_continuous(breaks = 1:8)+
    theme(axis.text.y = element_blank(),
          axis.title.y = element_blank(),
          axis.ticks = element_blank(),
          axis.title.x = element_text(size=15),
          axis.text.x = element_text(size=12),
          panel.background = element_rect(fill = greys[4], color = greys[4]),
          plot.background = element_rect(fill = greys[4], color = greys[4]),
          legend.background = element_rect(fill = greys[4], color = greys[4]),
          legend.box.background = element_rect(fill = greys[4], color = greys[4]), 
          panel.grid = element_blank())+
    scale_y_continuous(expand=expansion(mult = c(0, 0.15)))
  
  if (!is.na(avg.fail.aca)){
    p<- p+
      geom_hline(yintercept =avg.fail.aca, col = pal[4], size=1)+   
      annotate(geom = "text", y= Inf, x=.6, 
               label= paste("Academy Avg Fail Rate:",round(avg.fail.aca, 3)*100, "%"),
               vjust=1, hjust=0, color= pal[4], size=4)
  }
  renderPlot(p)
}

### grades vs attendence
grade_att<- function(df){
  renderPlot(
  ggplot(df, aes(Attend, as.factor(Number_F), color =as.factor(Number_F) ))+
    geom_point(position = "jitter", size=2)+
    theme(legend.position = "none",
          panel.background = element_rect(fill = greys[4], color = greys[4]),
          plot.background = element_rect(fill = greys[4], color = greys[4]),
          legend.background = element_rect(fill = greys[4], color = greys[4]),
          legend.box.background = element_rect(fill = greys[4], color = greys[4]), 
          panel.grid = element_blank())+
    labs(x="Attendance", y="Number of Failing Grades")+
    scale_x_continuous(breaks = seq(0,100,20),
                       labels = paste(seq(0,100,20), "%", sep = ""))+
    scale_color_manual(values = rev(pal)))
}

## grades by eth
grades_eth <- function(df, avg.fail.school, avg.fail.aca = NA){
  df.eth<- df%>% count(ETHNICITY) 
  
  df.fails<- df %>% group_by(ETHNICITY)%>%
    count(grade) %>% 
    left_join(df.eth, by = c("ETHNICITY"))%>%
    mutate(rel_freq = n.x/n.y) %>% 
    filter(grade == "F")
  
  
  p<- ggplot(df.fails, aes(x= ETHNICITY, y=rel_freq))+
    geom_col(fill = pal[1], color = pal[4])+
    geom_hline(yintercept =avg.fail.school, col = pal[2], size = 1)+
    geom_text(aes(label = paste(round(rel_freq, 2)*100,"%")), 
              vjust = -.5, size = 5)+
    annotate(geom = "text", y= Inf, x=Inf, 
             label= paste("Avg Fail Rate:",round(avg.fail.school, 3)*100, "%"),
             vjust=1, hjust=1, color=pal[2], size=4)+
    theme(panel.background = element_rect(fill = greys[4], color = greys[4]),
          plot.background = element_rect(fill = greys[4], color = greys[4]),
          legend.background = element_rect(fill = greys[4], color = greys[4]),
          legend.box.background = element_rect(fill = greys[4], color = greys[4]), 
          panel.grid = element_blank(),
          axis.text.y = element_blank(),
          axis.title = element_blank(),
          axis.ticks = element_blank(),
          axis.text.x = element_text(size=10, angle = 0))+
    scale_y_continuous(expand=expansion(mult = c(0, 0.15)))
  
  if (!is.na(avg.fail.aca)){
    p<- p+
      geom_hline(yintercept =avg.fail.aca, col = pal[4], size=1)+   
      annotate(geom = "text", y= Inf, x=.6, 
               label= paste("Academy Avg Fail Rate:",round(avg.fail.aca, 3)*100, "%"),
               vjust=1, hjust=0, color= pal[4], size=4)
  }
  renderPlot(p)
}

## grades by ELL
grades_ell<- function(df, avg.fail.school, avg.fail.aca = NA){
  df.ELL<- df%>% count(ELL)  
  
  df.fails.ELL<- df %>% group_by(ELL)%>%
    count(grade) %>% 
    left_join(df.ELL, by = c("ELL"))%>%
    mutate(rel_freq = n.x/n.y) %>% 
    filter(grade == "F")
  
  p<- ggplot(df.fails.ELL, aes(x= ELL, y=rel_freq))+
    geom_col(fill = pal[1], color = pal[4])+
    geom_hline(yintercept =avg.fail.school, col = pal[2], size = 1)+
    geom_text(aes(label = paste(round(rel_freq, 3)*100,"%")), 
              vjust = -.5, size = 5)+
    theme(panel.background = element_rect(fill = greys[4], color = greys[4]),
          plot.background = element_rect(fill = greys[4], color = greys[4]),
          legend.background = element_rect(fill = greys[4], color = greys[4]),
          legend.box.background = element_rect(fill = greys[4], color = greys[4]), 
          panel.grid = element_blank(),
          axis.text.y = element_blank(),
          axis.title = element_blank(),
          axis.ticks = element_blank(),
          axis.text.x = element_text(size=10))+
    scale_y_continuous(expand=expansion(mult = c(0, 0.15)))
  
  if (!is.na(avg.fail.aca)){
    p<- p+
      geom_hline(yintercept =avg.fail.aca, col = pal[4], size=1)
  }
  renderPlot(p)
}


## grades by iep
grades_iep <- function(df, avg.fail.school, avg.fail.aca = NA){
  df.iep<- df%>% count(IEP)  
  
  df.fails.iep<- df %>% group_by(IEP)%>%
    count(grade) %>% 
    left_join(df.iep, by = c("IEP"))%>%
    mutate(rel_freq = n.x/n.y) %>% 
    filter(grade == "F")
  
  p<- ggplot(df.fails.iep, aes(x= IEP, y=rel_freq))+
    geom_col(fill = pal[1], color = pal[4])+
    geom_hline(yintercept =avg.fail.school, col = pal[2], size = 1)+
    geom_text(aes(label = paste(round(rel_freq, 3)*100,"%")), 
              vjust = -.5, size = 5)+
    theme(panel.background = element_rect(fill = greys[4], color = greys[4]),
          plot.background = element_rect(fill = greys[4], color = greys[4]),
          legend.background = element_rect(fill = greys[4], color = greys[4]),
          legend.box.background = element_rect(fill = greys[4], color = greys[4]), 
          panel.grid = element_blank(),
          axis.text.y = element_blank(),
          axis.title = element_blank(),
          axis.ticks = element_blank(),
          axis.text.x = element_text(size=12))+ 
    scale_y_continuous(expand=expansion(mult = c(0, 0.15)))
  
  if (!is.na(avg.fail.aca)){
    p<- p+
      geom_hline(yintercept =avg.fail.aca, col = pal[4], size=1)
  }
  renderPlot(p)
}


```


```{r data}
## colors, Blue, red, red2, blue 2, grey1, grey2, #1A1E4B
#pal <- c("#003399", "#990000", "#800000", "#002266", "#D1D2D4", "#F6F5F2")

# autumn 1
#pal<- c("#7F3800", "#b35701", "#e06706", "#3c4858", "#a9aaaf", "#dadbdc", "#000000")

#pal<- c("#621B3B",	"#801D30",	"#98531B",	"#B18728",	"#6D6513",	"#3F4610")
pal<- c("#733300", "#7F3800", "#B35701", "#96570A", 
        "#795712", "#5C571A", "#3E5622", "#172815")
greys<- c("#3c4858", "#a9aaaf", "#dadbdc", "#f2f5f7")

## Date
date<- ymd("2022-03-07")

#reset()

## Data
df <- read_csv("Data7.csv")[,2:54]
names(df) <- c("Status", "ID", "Last", "First", "Grade", "Academy", 
               "PAT", "IEP", "ELL", "ETHNICITY", "INT", "student_email", 
               "contact_email", "A", "B", "C", "D", "PASSING", "Fail", "Attend", 
               "Credits", "Teacher1", "Course1", "Gr1", "gr1_perc", "Teacher2", 
               "Course2", "Gr2", "gr2_perc", "Teacher3", "Course3", "Gr3", 
               "gr3_perc", "Teacher4", "Course4", "Gr4", "gr4_perc", "Teacher5", 
               "Course5", "Gr5", "gr5_perc", "Teacher6", "Course6", "Gr6", 
               "gr6_perc", "Teacher7", "Course7", "Gr7", "gr7_perc", "Teacher8",
               "Course8", "Gr8", "gr8_perc")

df<- df %>% filter(!is.na(ID)) %>% 
  mutate(name = paste(First, Last, sep = ""), 
         IEP = ifelse(is.na(IEP), FALSE, TRUE)) %>%
  distinct(name, .keep_all = T)%>%
  select(-c(Status, Last, First, student_email, contact_email,
            A,B,C,D,Fail, PASSING))%>%
  mutate(Attend = as.numeric(str_extract(Attend, "[0-9.]+")),
         Attend = ifelse(Attend >100, 100, Attend),
         Academy = ifelse(Academy == "Public srv", "Public Srv", Academy))

df_full<-bind_rows(
df %>% select(c(name, ID, Academy, Grade, PAT, IEP, ELL, ETHNICITY, Attend,
                Credits, teacher=Teacher1, course=Course1, grade=Gr1,
                percent=gr1_perc))%>%
  mutate(hour=1),
df %>% select(c(name, ID, Academy, Grade, PAT, IEP, ELL, ETHNICITY, Attend,
                Credits, teacher=Teacher2, course=Course2, grade=Gr2,
                percent=gr2_perc))%>%
  mutate(hour=2),
df %>% select(c(name, ID, Academy, Grade, PAT, IEP, ELL, ETHNICITY, Attend,
                Credits, teacher=Teacher3, course=Course3, grade=Gr3,
                percent=gr3_perc))%>% 
  mutate(hour=3),
df %>% select(c(name, ID, Academy, Grade, PAT, IEP, ELL, ETHNICITY, Attend,
                Credits, teacher=Teacher4, course=Course4, grade=Gr4, 
                percent=gr4_perc))%>%
  mutate(hour=4),
df %>% select(c(name, ID, Academy, Grade, PAT, IEP, ELL, ETHNICITY, Attend,
                Credits, teacher=Teacher5, course=Course5, grade=Gr5, 
                percent=gr5_perc))%>%
  mutate(hour=5),
df %>% select(c(name, ID, Academy, Grade, PAT, IEP, ELL, ETHNICITY, Attend, Credits, 
                teacher=Teacher6, course=Course6, grade=Gr6, percent=gr6_perc))%>%
  mutate(hour=6),
df %>% select(c(name, ID, Academy, Grade, PAT, IEP, ELL, ETHNICITY, Attend, Credits, 
                teacher=Teacher7, course=Course7, grade=Gr7, percent=gr7_perc))%>%
  mutate(hour=7),
df %>% select(c(name, ID, Academy, Grade, PAT, IEP, ELL, ETHNICITY, Attend, Credits, 
                teacher=Teacher8, course=Course8, grade=Gr8, percent=gr8_perc))%>%
  mutate(hour=8)) %>% 
  mutate(grade = ifelse(grade=="_", NA, grade),
    grade = factor(grade, 
    levels = c("A", "A-","B+","B","B-","C+","C","C-","D+","D","D-",  "F")),
    percent = ifelse(percent == "_" | is.na(percent), NA, percent),
    percent = as.numeric(percent),
    Attend = as.numeric(str_extract(Attend, "[0-9.]+")),
    ETHNICITY = ifelse(is.na(ETHNICITY), "U", ETHNICITY),
    ETHNICITY = factor(ETHNICITY, 
                       levels = c("A","B", "H", "M", "P", "W", "I", "U"),
                       labels = c("Asian", "Black", "Hispanic", "Mixed",
                                  "Pacific Islander", "White", "Indigenous",
                                  "Unlisted"))
    )


```


Grades {data-navmenu="Entire School" data-icon="fa-list"}
======================================================


Column {data-width=650}
-----------------------------------------------------------------------


### Timeseries
```{r}
grades.df<- tsgrades_update("school_ts.RDS", df_full, date)

tsgrades_plot(grades.df)
```

Column {data-width=350}
-----------------------------------------------------------------------

### Grades 

```{r}
#summary(df1$grade)
grades_bar(df_full)
```

### By Grade level

```{r}
#summary(df1$grade)
grades_grade(df_full)
```


Attendance {data-navmenu="Entire School" data-icon="fa-list"}
=======================================================================

Column {data-width=500}
-----------------------------------------------------------------------
### Attendance
```{r}
df_att<- att_data(df_full)
att.df<- att_update("att_ts.RDS", df_att)

#att.df<- att

att_ts_plot(att.df)
```

### By Ethnicity
```{r}
att_eth(df_att)
```

Column {data-width=500}
-----------------------------------------------------------------------
### By Grade
```{r}
att_grade(df_att)
```

### By IEP

```{r}
att_iep(df_att)
```

Failing Grades {data-navmenu="Entire School" data-icon="fa-list"}
=======================================================================


Column {data-width=650}
-----------------------------------------------------------------------
### Failing Grades per Student
```{r}
df.f<-df_full %>% 
  mutate(grade = substring(grade,0,1))%>%
  group_by(name)%>%
  count(grade)%>%
  pivot_wider(names_from = grade, values_from = n)%>%
  mutate(across(everything(), ~ifelse(is.na(.x), 0, .x)))%>%
  select("name", "A", "B", "C", "D", "F")%>%
  rename(Name = name, Number_F = `F`)%>%
  inner_join(df%>%select(name,Attend, Academy, Grade), by = c("Name"="name"))

#knitr::kable(df.f)



fail_count(df.f)
```

Column {data-width=350}
-----------------------------------------------------------------------

### Hour

```{r}
avg.fail.school<- nrow(df_full%>% filter(grade=="F"))/nrow(df_full)

fail_hour(df_full, avg.fail.school)
```

### Failing Grades Compared to Attendance 


```{r}
grade_att(df.f)
```




Failing Grades by Demographics {data-navmenu="Entire School" data-icon="fa-list"}
=========================================================================

Column {data-width=650}
-----------------------------------------------------------------------
### Ethnicity

```{r}
grades_eth(df_full, avg.fail.school)
```



Column {data-width=350}
-----------------------------------------------------------------------

### ELL Status

```{r}
grades_ell(df_full, avg.fail.school)
```

### IEP

```{r}
grades_iep(df_full, avg.fail.school)
```

Top Students {data-navmenu="Entire School" data-icon="fa-list"}
===========================================================

```{r}
df.avg.gr<- df_full %>%
  mutate(percent = ifelse(percent >100, 100, percent)) %>%
  group_by(name)%>%
  summarise(Avg_Grd=mean(percent, na.rm=T))%>%
  arrange(desc(Avg_Grd))%>%
  rename(Name = name,
         `Average Grade` = Avg_Grd)

df.avg.gr %>% 
  mutate(`Average Grade` = round(`Average Grade`,1))%>%
datatable(extensions = "Buttons",
          options = list(dom = "lfrtipB",
                         buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                         lengthMenu = list(c(10,25,50,-1),
                                           c(10,25,50,"All"))))%>%
  formatStyle(names(df.avg.gr)[2], 
              background = styleColorBar(c(0,100), 'lightblue'),
              backgroundSize = '98% 60%',
              backgroundRepeat = 'no-repeat',
              backgroundPosition = 'center')
```

Student Data {data-navmenu="Entire School" data-icon="fa-list"}
=========================================================================


```{r}
df.f1<- df.f %>% rename(`F` = Number_F,
                Attendance = Attend)%>%
  select(c(1,9,8,2:7))
#formattable(df.f, 
#            align = c("l", "c", "r"),
#            list(Name = formatter(
#              "span", style = ~ style(color = "black",font.weight = "bold")),
#              `Number of Failing Classes` = color_tile(pal[1], pal[2]),
#              Attendance = color_bar(customGreen0)
#              ))

brks <- 0:8
brks2 <- seq(0,100,10)
clrs1 <- sequential_hcl(n=10, palette = "Greens", rev = T)%>% lighten(amount = 0.25)
clrs2 <- sequential_hcl(n=10, palette = "OrRd", rev = T)%>% lighten(amount = 0.25)
clrs3 <- sequential_hcl(n=10, palette = "Reds", rev = T)%>% lighten(amount = 0.25)

datatable(df.f1, filter = 'top', rownames = FALSE, 
          extensions = "Buttons",
          options = list(dom = "lrtipB",
                         buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                         lengthMenu = list(c(10,25,50,-1),
                                           c(10,25,50,"All")))) %>%
  formatStyle(names(df.f1)[4:5], backgroundColor = styleInterval(brks, clrs1))%>%
  formatStyle(names(df.f1)[6:7], backgroundColor = styleInterval(brks, clrs2))%>%
  formatStyle(names(df.f1)[8], backgroundColor = styleInterval(brks, clrs3))%>%
  formatStyle(names(df.f1)[9], 
              background = styleColorBar(c(0,100), "lightblue"),
              backgroundSize = '98% 70%',
              backgroundRepeat = 'no-repeat',
              backgroundPosition = 'center',)
```





Grades {data-navmenu="Academy 1" data-icon="fa-list"}
======================================================

Column {data-width=650}
-----------------------------------------------------------------------

### Timeseries

```{r}
df1 <- df_full %>% filter(Academy == "academy_1")
grades.df<- tsgrades_update("aca1_ts.RDS", df1, date)

tsgrades_plot(grades.df)
```

Column {data-width=350}
-----------------------------------------------------------------------

### Grades 

```{r}
grades_bar(df1)
```

### By Grade level

```{r}
grades_grade(df1)
```


Failing Grades {data-navmenu="Academy 1" data-icon="fa-list"}
=======================================================================


Column {data-width=650}
-----------------------------------------------------------------------
### Failing Grades per Student
```{r}
df.f<-df1 %>% group_by(name)%>%
  count(grade)%>% 
  filter(grade == "F")%>%
  arrange(desc(n))%>%
  select(name, n)
names(df.f)<- c("Name", "Number_F")
df.f<-df.f %>% inner_join(df%>%select(name,Attend), by = c("Name"="name"))

fail_count(df.f)
```

Column {data-width=350}
-----------------------------------------------------------------------

### Hour

```{r}
avg.fail<- nrow(df1%>% filter(grade=="F"))/nrow(df1)

fail_hour(df1, avg.fail.school, avg.fail)
```

### Failing Grades Compared to Attendance 


```{r}
grade_att(df.f)
```

Failing Grades by Demographics {data-navmenu="Academy 1" data-icon="fa-list"}
=========================================================================

Column {data-width=650}
-----------------------------------------------------------------------
### Ethnicity

```{r}
avg.fail<- nrow(df1%>% filter(grade=="F"))/nrow(df1)

grades_eth(df1, avg.fail.school, avg.fail)
```



Column {data-width=350}
-----------------------------------------------------------------------

### ELL Status

```{r}
grades_ell(df1, avg.fail.school, avg.fail)
```

### IEP

```{r}
grades_iep(df1, avg.fail.school, avg.fail)
```

Top Students {data-navmenu="Academy 1" data-icon="fa-list"}
===========================================================

```{r}
df.avg.gr<- df1 %>%
  mutate(percent = ifelse(percent >100, 100, percent)) %>%
  group_by(name)%>%
  summarise(Avg_Grd=mean(percent, na.rm=T))%>%
  arrange(desc(Avg_Grd))%>% 
  mutate(Avg_Grd = round(Avg_Grd,1))%>%
  rename(Name = name, 
                     `Average Grade` = Avg_Grd)

df.avg.gr %>%
datatable(extensions = "Buttons",
          options = list(dom = "lfrtipB",
                         buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                         lengthMenu = list(c(10,25,50,-1),
                                           c(10,25,50,"All"))))%>%
  formatStyle(names(df.avg.gr)[2], 
              background = styleColorBar(c(0,100), 'lightblue'),
              backgroundSize = '98% 60%',
              backgroundRepeat = 'no-repeat',
              backgroundPosition = 'center')
```









Grades {data-navmenu="Academy 2" data-icon="fa-list"}
======================================================

Column {data-width=650}
-----------------------------------------------------------------------

### Timeseries

```{r}
df1 <- df_full %>% filter(Academy == "academy_2")
grades.df<- tsgrades_update("aca2_ts.RDS", df1, date)

tsgrades_plot(grades.df)
```

Column {data-width=350}
-----------------------------------------------------------------------

### Grades 

```{r}
grades_bar(df1)
```

### By Grade level

```{r}
grades_grade(df1)
```


Failing Grades {data-navmenu="Academy 2" data-icon="fa-list"}
=======================================================================


Column {data-width=650}
-----------------------------------------------------------------------
### Failing Grades per Student
```{r}
df.f<-df1 %>% group_by(name)%>%
  count(grade)%>% 
  filter(grade == "F")%>%
  arrange(desc(n))%>%
  select(name, n)
names(df.f)<- c("Name", "Number_F")
df.f<-df.f %>% inner_join(df%>%select(name,Attend), by = c("Name"="name"))

fail_count(df.f)
```

Column {data-width=350}
-----------------------------------------------------------------------

### Hour

```{r}
avg.fail<- nrow(df1%>% filter(grade=="F"))/nrow(df1)

fail_hour(df1, avg.fail.school, avg.fail)
```

### Failing Grades Compared to Attendance 


```{r}
grade_att(df.f)
```

Failing Grades by Demographics {data-navmenu="Academy 2" data-icon="fa-list"}
=========================================================================

Column {data-width=650}
-----------------------------------------------------------------------
### Ethnicity

```{r}
avg.fail<- nrow(df1%>% filter(grade=="F"))/nrow(df1)

grades_eth(df1, avg.fail.school, avg.fail)
```



Column {data-width=350}
-----------------------------------------------------------------------

### ELL Status

```{r}
grades_ell(df1, avg.fail.school, avg.fail)
```

### IEP

```{r}
grades_iep(df1, avg.fail.school, avg.fail)
```

Top Students {data-navmenu="Academy 2" data-icon="fa-list"}
===========================================================

```{r}
df.avg.gr<- df1 %>%
  mutate(percent = ifelse(percent >100, 100, percent)) %>%
  group_by(name)%>%
  summarise(Avg_Grd=mean(percent, na.rm=T))%>%
  arrange(desc(Avg_Grd))%>% 
  mutate(Avg_Grd = round(Avg_Grd,1))%>%
  rename(Name = name, 
                     `Average Grade` = Avg_Grd)

df.avg.gr %>%
datatable(extensions = "Buttons",
          options = list(dom = "lfrtipB",
                         buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                         lengthMenu = list(c(10,25,50,-1),
                                           c(10,25,50,"All"))))%>%
  formatStyle(names(df.avg.gr)[2], 
              background = styleColorBar(c(0,100), 'lightblue'),
              backgroundSize = '98% 60%',
              backgroundRepeat = 'no-repeat',
              backgroundPosition = 'center')
```








Grades {data-navmenu="Academy 3" data-icon="fa-list"}
======================================================

Column {data-width=650}
-----------------------------------------------------------------------

### Timeseries

```{r}
df1 <- df_full %>% filter(Academy == "academy_3")
grades.df<- tsgrades_update("aca3_ts.RDS", df1, date)

tsgrades_plot(grades.df)
```

Column {data-width=350}
-----------------------------------------------------------------------

### Grades 

```{r}
grades_bar(df1)
```

### By Grade level

```{r}
grades_grade(df1)
```


Failing Grades {data-navmenu="Academy 3" data-icon="fa-list"}
=======================================================================


Column {data-width=650}
-----------------------------------------------------------------------
### Failing Grades per Student
```{r}
df.f<-df1 %>% group_by(name)%>%
  count(grade)%>% 
  filter(grade == "F")%>%
  arrange(desc(n))%>%
  select(name, n)
names(df.f)<- c("Name", "Number_F")
df.f<-df.f %>% inner_join(df%>%select(name,Attend), by = c("Name"="name"))

fail_count(df.f)
```

Column {data-width=350}
-----------------------------------------------------------------------

### Hour

```{r}
fail_hour(df1, avg.fail.school, avg.fail)
avg.fail<- nrow(df1%>% filter(grade=="F"))/nrow(df1)
```

### Failing Grades Compared to Attendance 


```{r}
grade_att(df.f)
```

Failing Grades by Demographics {data-navmenu="Academy 3" data-icon="fa-list"}
=========================================================================

Column {data-width=650}
-----------------------------------------------------------------------
### Ethnicity

```{r}
avg.fail<- nrow(df1%>% filter(grade=="F"))/nrow(df1)
grades_eth(df1, avg.fail.school, avg.fail)
```



Column {data-width=350}
-----------------------------------------------------------------------

### ELL Status

```{r}
grades_ell(df1, avg.fail.school, avg.fail)
df.ELL<- df1%>% count(ELL)  
```

### IEP

```{r}
grades_iep(df1, avg.fail.school, avg.fail)
```

Top Students {data-navmenu="Academy 3" data-icon="fa-list"}
===========================================================

```{r}
df.avg.gr<- df1 %>%
  mutate(percent = ifelse(percent >100, 100, percent)) %>%
  group_by(name)%>%
  summarise(Avg_Grd=mean(percent, na.rm=T))%>%
  arrange(desc(Avg_Grd))%>% 
  mutate(Avg_Grd = round(Avg_Grd,1))%>%
  rename(Name = name, 
                     `Average Grade` = Avg_Grd)

df.avg.gr %>%
datatable(extensions = "Buttons",           options = list(dom = "lfrtipB",                          buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),                          lengthMenu = list(c(10,25,50,-1),                                            c(10,25,50,"All"))))%>%
  formatStyle(names(df.avg.gr)[2], 
              background = styleColorBar(c(0,100), 'lightblue'),
              backgroundSize = '98% 60%',
              backgroundRepeat = 'no-repeat',
              backgroundPosition = 'center')
```





